Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-29 doc/PRF2022/PRF_main.tex
yny

In this work we focus on collective hydrodynamics of immobile (non self-propelling)
amphiphilic JPs in a viscous fluid under an imposed far-field flow. The
amphiphilic JP has a hydrophobic surface on one side and a hydrophilic
surface on the other side \cite{doi:10.1021/la503455h}. The many-body
hydrodynamics of amphiphilic Janus particles assembled as vesicles
(self-enclosed bilayers of JPs) suspended in a viscous fluid in the
inertialess regime (zero Reynolds number) has been studied using
boundary integral numerical simulations~\cite{Fu20,Fu2022_JFM}. The
dynamics of the JP suspension arises spontaneously from the combination of long-range
hydrodynamic interaction and non-local interactions between JPs through
the distribution of a hydrophobic attraction potential (HAP).
%
In a quiescent flow, a JP suspension self-assembles into micelles and
bilayers of JPs that provide an alternative means for computing the
mechanical moduli of a colloidal membrane in numerical
simulations~\cite{NaTr00, Fu20, KrFiGuKaHa13}. Under background flows,
the hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs)
exhibit many familiar behaviors of a vesicle: elongation and alignment
along the extensional direction, tank-treading, and rupture of a vesicle
under shear flow~\cite{Fu2022_JFM, grandmaison_brancherie_salsac_2021,
D2SM00179A,keller_skalak_1982, Finken08, Shaqfeh11}.

Molecular dynamics (MD) and Monte Carlo simulations provide another
means for simulating the interaction between JPs, solvents, and
substrates~\cite{Brandner2019, Baniketal2021,
HongCacciutoLuijtenGranick2008, C9NR05885K}. In these methods
pair-potentials are used to describe the interaction between JPs, for
example by prescribing angle dependent forces and torques that bring the
hydrophobic sides of two amphiphilic JPs into opposition. On the other
hand, the HAP formulation of the present work has attractive, long-range
forces and torques, and they are instead derived from a boundary value
problem for the molecular structure of water~\cite{Ma77, GoHaKo94,
ErLjCl89, Lietal05, Israelachvili80}. Unlike in MD or Monte Carlo
simulations, the HAP interactions are nonadditive~\cite{Fu20}, so that
the interactions between a pair of JPs is affected by the presence of
other particles. As such, the HAP is a phase-field function that
represents the properties of the solvent in the presence of JPs. Such
approach falls into the category of work that considers particles as a
discretization of a continuum problem~\cite{HongWang2021_arXiv}.

>>>>

In this work we focus on collective hydrodynamics of immobile (non self-propelling)
JPs in a viscous fluid under an imposed far-field flow. The
amphiphilic JP has a hydrophobic surface on one side and a hydrophilic
surface on the other side \cite{doi:10.1021/la503455h}. The many-body
hydrodynamics of amphiphilic Janus particles assembled as vesicles
(self-enclosed bilayers of JPs) suspended in a viscous fluid in the
inertialess regime (zero Reynolds number) has been studied using
boundary integral numerical simulations~\cite{Fu20,Fu2022_JFM}. The
dynamics of the JP suspension arises spontaneously from the combination of long-range
hydrodynamic interaction and non-local interactions between JPs through
the distribution of a hydrophobic attraction potential (HAP).
%
In a quiescent flow, an amphiphilic JP suspension self-assembles into micelles and
bilayers of JPs that provide an alternative means for computing the
mechanical moduli of a colloidal membrane in numerical
simulations~\cite{NaTr00, Fu20, KrFiGuKaHa13}. Under background flows,
the hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs)
exhibit many familiar behaviors of a vesicle: elongation and alignment
along the extensional direction, tank-treading, and rupture of a vesicle
under shear flow~\cite{Fu2022_JFM, grandmaison_brancherie_salsac_2021,
D2SM00179A,keller_skalak_1982, Finken08, Shaqfeh11}.

Molecular dynamics (MD) and Monte Carlo simulations provide another
means for simulating the interaction between amphiphilic JPs, solvents, and
substrates~\cite{Brandner2019, Baniketal2021,
HongCacciutoLuijtenGranick2008, C9NR05885K}. In these methods
pair-potentials are used to describe the interaction between amphiphilic JPs
by prescribing angle dependent forces and torques that bring the
hydrophobic sides of two amphiphilic JPs into opposition. On the other
hand, the HAP formulation of the present work has attractive, long-range
forces and torques, and they are instead derived from a boundary value
problem for the molecular structure of water~\cite{Ma77, GoHaKo94,
ErLjCl89, Lietal05, Israelachvili80}. Unlike in MD or Monte Carlo
simulations, the HAP interactions are nonadditive~\cite{Fu20}, so that
the interactions between a pair of JPs is affected by the presence of
other particles. As such, the HAP is a phase-field function that
represents the properties of the solvent in the presence of JPs. Such
approach falls into the category of work that considers particles as a
discretization of a continuum problem~\cite{HongWang2021_arXiv}.
